### 2021-02-22 main.tex
docasne vypinam svg plot
Add a WIP content into Future work

@@

\begin{figure}[h]
\caption{The dependence of preprocessing time on the number of nodes in the problem graph on 1000 random validation problems}
\label{fig:preprocessing}
\centering
\includesvg[width=\textwidth]{preprocessing}
% Source: https://docs.google.com/spreadsheets/d/1GujYNEtETpC3jk4iyENLjptv8mDmI5f1ZEhbmwtqnPM/edit#gid=394425425&fvid=659935521
% Experiment: VML-715
\end{figure}

>>>>

Reinforcement learning will allow using a trained recommender to generate data from harder problems.

In our experiments, too much attention is spent on uninteresting examples.
We learn to order pairs of non-optimal precedences.
However, if the recommender ordered a non-optimal pair wrong, it could still produce the optimum precedence correctly.
Besides, we train from pairs of successful runs that only differ in number of iterations.

@@

\begin{figure}[h]
\caption{The dependence of preprocessing time on the number of nodes in the problem graph on 1000 random validation problems}
\label{fig:preprocessing}
\centering
% \includesvg[width=\textwidth]{preprocessing}
% Source: https://docs.google.com/spreadsheets/d/1GujYNEtETpC3jk4iyENLjptv8mDmI5f1ZEhbmwtqnPM/edit#gid=394425425&fvid=659935521
% Experiment: VML-715
\end{figure}
